Kernel Phase and Coronagraphy with Automatic Differentiation

### 2020-05-13 ms.tex
Updates from Overleaf

To see the effect of the `ghost' introduced by the neutral density filter used to observe such bright stars, we calculate kernel phase `colinearity' maps as in \citet{martinache20}, shon in Figure~\ref{colinearity}.

>>>>

To see the effect of the `ghost' introduced by the neutral density filter used to observe such bright stars, we calculate kernel phase `colinearity' maps as in \citet{martinache20}, shown in Figure~\ref{colinearity}.
